From Freebase to Wikidata: The Great Migration

### 2015-10-07 paper.tex
Converts freebase-cvt-obama to PDF
Reworked Section 3.1.

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/freebase-cvt-obama.png}
\caption{\todo{Crop, get PDF version} Example of CVT: presidency of Barack Obama}
\label{fig:cvt-obama}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
\caption{An example of Wikidata statement (from
	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig:statement}
\end{figure}

@@

Migrating data from Freebase to Wikidata faced a~number of challenges:

@@

The first challenge is regarding the licenses under which the datasets are published.
Wikidata is published under a~Creative Commons~0 (CC0) license (similar to the public domain),
while Freebase is under a~Creative Commons By license and contains data
imported from external projects not owned by Google,
like images or descriptions extracted from Wikipedia.
In a~first step we filtered the Freebase dump from this kind of content
before being able to have a~dump that Google could relicense under CC0.
This step reduces the number of republishable Freebase facts by about 42M~facts.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.pdf}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0cm 3cm 0cm 5cm, width=8.45 cm]{img/freebase-cvt-obama.pdf}
\caption{Exemplary Compound Value Type (CVT) in Freebase: Presidency of Barack Obama}
%The source is https://docs.google.com/document/d/1ELrBtxxs4ghhe7FloTUnhvpD3f7RFczT7UfxahAfjgE/edit
\label{fig:cvt-obama}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
\caption{Wikidata nomenclature illustrated with an example (Source:
	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig:statement}
\end{figure}

@@

During our ongoing efforts with the migration of Freebase to Wikidata
we were faced with a~number of technical and non-technical challenges
that we will outline in the following.

@@

The first challenge concerns the licenses under which the datasets are published.
Wikidata is published under a~Creative Commons~0 (CC0~1.0) license
that effectively puts the data in the public domain,
whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
and contains data imported from external projects not owned by Google,
like images or descriptions extracted from Wikipedia.
In a~first step, we filtered the Freebase dump for this kind of content
before being able to create a~dump that we could relicense under CC0~1.0.
This step reduced the number of Freebase facts that could be republished by about 42M~facts
from 3~billion facts in the original corpus.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.pdf}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
%Data sheet: https://docs.google.com/spreadsheets/d/1jYGVIqAmyouHKjvhM6FbpgTD8bb5tkJy9PEMELkuMwo/edit
\end{figure}
